onsetsync: An R Package for Onset Synchrony Analysis

### 2023-09-09 README.Rmd
Improvements based on reviews
version 0.5.0

```{r,eval=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("tuomaseerola/onsetsync")
```

@@

>>>>

```{r,eval=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE)
```

@@

Read the [community guidelines](CONTRIBUTING.md) for contributing to the package or asking questions.

### 2023-09-09 paper/paper.Rmd
version 0.5.0

```{r secret_load, eval=TRUE, echo=FALSE}
# LOADS THIS SECRECTLY FROM THE LOCAL FOLDER
library(onsetsync)
ver <- packageVersion('onsetsync')
```

@@

```{r availability,eval=FALSE}
library(devtools)
devtools::install_github("tuomaseerola/onsetsync")
library(onsetsync)
```

>>>>

```{r secret_load, eval=TRUE, echo=FALSE}
# LOADS THIS SECRECTLY FROM THE LOCAL FOLDER
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE)
#library(onsetsync)
ver <- packageVersion('onsetsync')
```

@@

```{r availability,eval=FALSE}
library(devtools)
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE)
library(onsetsync)
```
